On the Synchronization Power of the Openflow Data Plane

### 2015-04-12 inband-sync.tex
aaa

\emph{FlowMod} is the main messages used in Openflow 
to update the switch configuration. 
In a nutshell, \emph{FlowMod} specifies a new flow entry or the modifications to existing flow entries.
The main properties of each flow entry are: 1) A match defined by a ternary patterns (a value and a mask) over packet header fields, 2) Instructions defined by  a list of modifications to packet action set 3) a cookie value used to reference a single or multiple packets.

@@

The Openflow bundle can be seen as a ``mini-transaction'':
a bundles aggregates multiple control messages (add, remove, and modify rule)
into one, so that either all of the control messages are
processed, or none of them is. In particular, if, for some reason, the
configuration request contained in one of the bundled messages cannot
be processed, all the other requests  are rejected and an error
message is sent to the controller that issued them.
This bundled processing can be, when properly configured, done in a
\emph{packet-atomic} way, so that each packet is processed according
to the switch configuration either \emph{before} or \emph{after} the
request was processed.
If used together with the CHECK\_OVERLAP flag, the bundle command also returns a reason 
if the modification failed: the failed command in the bundle:
a CHECK\_OVERLAP flag can be defined for each command in the bundle.
\liron{these last two sentences are not cleaar}

>>>>

\emph{FlowMod} is the main messages used in Openflow 
to update the switch configuration. 
In a nutshell, \emph{FlowMod} specifies a new flow entry or modifications to existing flow entries.
A flow entry is mainly composed from a match defined by a ternary patterns (a value and a mask) over packet header fields, and from actions.

@@

The Openflow bundle can be seen as a ``mini-transaction'':
a bundles aggregates multiple control commands (e.g., FlowMod messages)
into one execution, so that either all of the control messages are
processed, or none of them is. In particular, if, for some reason, the
configuration request contained in one of the bundled messages cannot
be processed, all the other requests  are rejected and an error
message is sent to the controller that issued them.
This bundled processing can be, when properly configured, done in a
\emph{packet-atomic} way, so that each packet is processed according
to the switch configuration either \emph{before} or \emph{after} the
request was processed.
If used together with the CHECK\_OVERLAP flag, the bundle command also returns a reason 
if the modification failed: the failed command in the bundle:
a CHECK\_OVERLAP flag can be defined for each command in the bundle.
\liron{these last two sentences are not cleaar}
